---
title: "Dairy Farm Benchmark Report"
output: pdf_document
date: "`r format(Sys.time(), '%B %d, %Y')`"
params:
  q_milk: NA
  purchased_feed: NA
  homegrown_feed: NA 
  exp_l_family: NA
  exp_l_hired: NA
  capital: NA
  misc: NA
  n.row: NA
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE,warning = FALSE)
options(scipen=1, digits=2)
library(tidyverse)
library(googlesheets)
library(Benchmarking)
library(knitr)
library(kableExtra)
library(gridExtra)

#n.row=23

sheet <- gs_title("data_efficiency")
# Read the data
testData <- gs_read_csv(sheet)
testData <- testData[1:params$n.row, ]

testData<-testData %>% 
  mutate(feed = homegrown_feed+purchased_feed) %>% 
  mutate(labour = exp_l_family+exp_l_hired) 
  
  
  
X <- testData[, 2:7]
X <- data.matrix(X)
Y <- testData[, 1]
Y <- data.matrix(Y)
DEA.results <- dea(X, Y,  RTS = 3)

eff.scores.org <- DEA.results$eff
testData$eff.score <-eff.scores.org
myscore = eff.scores.org[params$n.row]
eff.scores <- sort(eff.scores.org)

d.plot <- data.frame(n.farm = 1:length(eff.scores), es = eff.scores)
n.myfarm <- d.plot$n.farm[which.min(abs(eff.scores - myscore))]
d.myfarm <-
data.frame(x = n.myfarm,
y = myscore,
lab = paste0("My Farm: ", round(myscore, 3)))


# feed efficiency ---------------
    X.f<-testData[,2]
    X.f<-data.matrix(X.f)
    #Y<-testData[,1]
    #Y<-data.matrix(Y)
    DEA.results.f <- dea(X.f, Y,  RTS=3);
    eff.scores.f <- DEA.results.f$eff;
    testData$eff.score.f <-eff.scores.f
    myscore.f = eff.scores.f[params$n.row]
    eff.scores.f <- sort(DEA.results.f$eff);
    d.plot.f<-data.frame(n.farm=1:length(eff.scores.f),es=eff.scores.f)
    n.myfarm.f<-d.plot.f$n.farm[which.min(abs(eff.scores.f-myscore.f))]
    d.myfarm.f<-data.frame(x=n.myfarm.f,y=myscore.f,lab=paste0("My Farm: ",round(myscore.f,3)))

# data of my farm---------------
    d.my<-testData[params$n.row,]
    
```
# Summary

The overall efficiency score provides a measure of how efficiently an operation converts all of its inputs (feed,
labour, capital, and miscellaneous expenses) into milk output (litres shipped). It is a measure of overall productivity of the
operation and allows for comparison to peers' operations as well as your own operation year-to-year in order to
track performance. The higher the score, the more efficiently the operation converts inputs into milk shipped.


Your operation's overall efficiency score is `r myscore`.
The most efficient performing operation has an overall efficiency score of `r max(eff.scores)`.
The average overall efficiency score for all operations is `r mean(eff.scores)`.


The feed efficiency score provides a measure of how efficiently an operation converts feed into milk shipped. Feed
expenses are often the highest variable cost for dairy operations and therefore a higher score may result lower costs
per litre of milk shipped. Feed consumption is also highly correlated with greenhouse gas emissions from bovine
animals. Therefore, herds with higher feed efficiency scores may produce lower levels of greenhouse gas emissions
than comparative herds with lower scores.


Your feed efficiency score is `r myscore.f`.
The most efficient performing operation has a feed efficiency score of `r max(eff.scores.f)`.
The average feed efficiency score for all operations is `r mean(eff.scores.f)`.


The following Table 1 provides a comparison between your operation, the average operation and the most efficient
performing operation. The far right column calculates the difference between your operation and the top 10 most efficient Operations.

```{r}
top10.data<- testData %>% 
  top_n(n = 10,wt =eff.score )

tb.op.compare<-data.frame(
  your.op = unlist(c(testData[params$n.row,"q_milk"],
              testData[params$n.row,"n_lactating_cows"],
              testData[params$n.row,"feed"],
              testData[params$n.row,"labour"],
              testData[params$n.row,"capital"],
              testData[params$n.row,"misc"]
              )),
  ave.op = c(
              mean(testData$q_milk),
              mean(testData$n_lactating_cows),
              mean(testData$feed),
              mean(testData$labour),
              mean(testData$capital),
              mean(testData$misc)
    
  ),
  top10 = c(
              mean(top10.data$q_milk),
              mean(top10.data$n_lactating_cows),
              mean(top10.data$feed),
              mean(top10.data$labour),
              mean(top10.data$capital),
              mean(top10.data$misc)
    
  )
)
rownames(tb.op.compare)<-c("Milk Shipped (L)",
                           "Number of Lactating Cows",
                           "Feed Expenses ($)",
                           "Labour Expenses ($)",
                           "Capital Expenses ($)",
                           "Miscellaneous Expenses ($)"
)
tb.op.compare$diff<-tb.op.compare$your.op- tb.op.compare$top10
colnames(tb.op.compare)<-c(
  "My Operation",
  "Average Operation",
  "Top 10 Operations",
  "Difference"
)


tb.op.compare %>%
  kable(align = 'c',caption = "Operation Comparison") %>%
  kable_styling()
```

\newpage
# Productivity Measures
The following Table 2 provides a milk output per cow and cost per litre comparison between your operation, the
average operation and the top 10 most performing operations.

The following Figures visually displays the information above.

```{r}
milk_output<-testData %>% 
      mutate(total_cost = purchased_feed+
               homegrown_feed+
               capital+
               exp_l_family+
               exp_l_hired+
               misc) %>% 
      mutate(milk_per_cow = q_milk/n_lactating_cows) %>% 
      mutate(feed_per_litre_milk = (purchased_feed+homegrown_feed)/q_milk) %>% 
      mutate(capital_per_litre_milk = capital/q_milk) %>% 
      mutate(labour_per_litre_milk = (exp_l_family+exp_l_hired)/q_milk) %>% 
      mutate(misk_per_litre_milk = misc/q_milk) %>% 
      mutate(ttcost_per_litre_milk = total_cost/q_milk) %>% 
      select(milk_per_cow,
             feed_per_litre_milk,
             capital_per_litre_milk,
             labour_per_litre_milk,
             misk_per_litre_milk,
             ttcost_per_litre_milk,
             eff.score)

top10<-milk_output %>% 
      top_n(10,wt = eff.score) %>% 
      colMeans() %>% 
      unlist()
    
tb_milk_output_data<-data.frame(
      `My Operation`=unlist(milk_output[params$n.row,1:6]),
      `Average of All Operations`=unlist(colMeans(milk_output[,1:6])),
      top10=top10[1:6],
      row.names =c("Milk Output Per Cow (L)",
                   "Cost of Feed Per Litre Milk ($)",
                   "Cost of Capital Per Litre Milk ($)",
                   "Cost of Labour Per Litre Milk ($)",
                   "Cost of Miscellaneous Per Litre Milk ($)",
                   "Total Cost per Litre Milk ($)")
    )
    colnames(tb_milk_output_data)<-c("My",
                                     "Average",
                                     "Top 10"
    )
    
tb_milk_output_data %>%
  kable(align = 'c',caption = "Milk Output and Cost Per Litre Comparison") %>%
  kable_styling()

d.plot.per<-data.frame(t(tb_milk_output_data))
d.plot.per$name<-rownames(d.plot.per)
d.plot.per$name<-factor(d.plot.per$name,
                        levels = c("My",
                                   "Average",
                                   "Top 10"))

p1<-ggplot(d.plot.per)+
  geom_col(aes(x = name, y=Milk.Output.Per.Cow..L.,fill=name))+
  labs(x="",y="Milk Output Per Cow (L)")+
  guides(fill=FALSE)

p2<-ggplot(d.plot.per)+
  geom_col(aes(x = name, y=Cost.of.Feed.Per.Litre.Milk....,fill=name))+
  labs(x="",y="Feed Per Litre Milk ($)")+
  guides(fill=FALSE)

p3<-ggplot(d.plot.per)+
  geom_col(aes(x = name, y=Cost.of.Capital.Per.Litre.Milk....,fill=name))+
  labs(x="",y="Capital Per Litre Milk ($)")+
  guides(fill=FALSE)

p4<-ggplot(d.plot.per)+
  geom_col(aes(x = name, y=Cost.of.Labour.Per.Litre.Milk....,fill=name))+
  labs(x="",y="Labour Per Litre Milk ($)")+
  guides(fill=FALSE)

p5<-ggplot(d.plot.per)+
  geom_col(aes(x = name, y=Cost.of.Miscellaneous.Per.Litre.Milk....,fill=name))+
  labs(x="",y="Miscellaneous Per Litre Milk ($)")+
  guides(fill=FALSE)

p6<-ggplot(d.plot.per)+
  geom_col(aes(x = name, y=Total.Cost.per.Litre.Milk....,fill=name))+
  labs(x="",y="Total Cost per Litre Milk ($)")+
  guides(fill=FALSE)

grid.arrange(p1, p2, p3, p4,p5,p6, 
             nrow = 2,
             top = "Milk Output and Cost Per Litre Comparison")


```

\newpage
# Milk Yield Comparison

Your Milk Yield is `r d.my$q_milk/d.my$n_lactating_cows` litres per cow.
The average milk yield of all farms is `r mean(testData$q_milk/testData$n_lactating_cows)` litres per cow.

Milk Yield is calculated by dividing the total amount of milk shipped by the average number of milking cows in
the benchmark year. 

The following figure shows the distribution of milk yield per cow.  The milk yield per cow on your farm is marked in red. 
```{r}
ggplot()+
  geom_histogram(aes(testData$q_milk/testData$n_lactating_cows))+
  labs(x="Milk per Cow (L)", y="Number of Farms")+
  #geom_vline(xintercept =d.my$q_milk/d.my$n_lactating_cows,color="red")+
  geom_histogram(aes(d.my$q_milk/d.my$n_lactating_cows,fill="My farm"))+
  guides(fill=guide_legend(title=""))
```

# Overall Efficiency

```{r}
plot1<-ggplot() +
        geom_col(data = d.plot, aes(x = n.farm, y = es)) +
        geom_hline(
          data = d.plot,
          yintercept = myscore,
          lty = 3,
          col = "red"
        ) +
        labs(title = "Overall Efficiency Scores",
             x = "Farm", y = "Overall Efficiency Score") +
        geom_col(aes(x = n.myfarm, y = myscore), fill = "red")+
        geom_label(
          data = d.myfarm,
          aes(
            x = x,
            y = min(y+0.1,1),
            label = lab
            
          ),fill = "firebrick1",alpha=0.65,
          colour = "white",
          fontface = "bold",
          vjust = "inward", hjust = "inward"
        )
      plot1
```



# Feed Efficiency
```{r}
plot1<-ggplot() +
      geom_col(data = d.plot.f, aes(x = n.farm, y = es)) +
      geom_hline(
        data = d.plot.f,
        yintercept = myscore.f,
        lty = 3,
        col = "red"
      ) +
      labs(title = "Feed Efficiency Scores",
           x = "Farm", y = "Feed Efficiency Score") +
      geom_col(aes(x = n.myfarm.f, y = myscore.f), fill = "red")+
      geom_label(
        data = d.myfarm.f,
        aes(
          x = x,
          y = min(y+0.1,1),
          label = lab
          
        ),fill = "firebrick1",alpha=0.65,
        colour = "white",
        fontface = "bold",
        vjust = "inward", hjust = "inward"
      )
    plot1
```

